MCC Kids Model Predictions

### 2019-02-12 stats/kids/kids_model_predictions.Rmd

var ex3Data = dataFromR.ex3data
var modelParams = dataFromR.modelParams[0]
var ageConditions = dataFromR.ageConditions

var model = function(){
    var noise = uniformDrift({a: 0, b:1, width: 0.1})

    var conditionOutput = map(function(conditionInfo){

   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})

    display(JSON.stringify(ageSpecificParams))

    var speakerOptimality = ageSpecificParams.so_map

    var diff_priorReg = ageSpecificParams.diff_priorReg_map

    map(function(d){ 
      observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)

  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]

}, ageConditions)

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
)

>>>>

```{r}
noisyModelPredWebppl <- '
var levels = function(df, label){
  return _.uniq(_.map(df, label));
}
var ex3Data = dataFromR.ex3data
var modelParams = dataFromR.modelParams
var ageConditions = dataFromR.ageConditions
var model = function(){
  var noise = uniformDrift({a: 0, b:1, width: 0.1})
  var predict_by_age = function(age_bin){
    var conditionOutput = map(function(conditionInfo){
   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
    var speakerOptimality = age_bin.so_map

    var diff_priorReg = age_bin.diff_priorReg_map
    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]

    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
    var noisyRsaPredictions_diff_cong = addNoise(rsaPredictions_diff_cong, noise)
    map(function(d){ 
    observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)
  // display(conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment)
  // display(Math.exp(noisyRsaPredictions_diff_cong.score(1)))

  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]
  }, ageConditions)
  }
  var predictions_by_age = map(predict_by_age, modelParams)
  display(JSON.stringify(predictions_by_age))
  return predictions_by_age
}
'
```

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data %>% mutate(binned_age = as.numeric(as.character(binned_age))), 
             modelParams = model_params_by_age, 
             ageConditions = ageConditions),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
)
